Refining from the VHDL-AMS Hardware Description Language to the BON High-level Specification Language

### 2010-01-17 papers/BON_VHDL/paper.tex
Cleaning up some equations and LaTeX.

%======================================================================
%\thispagestyle{empty}
\begin{abstract}

@@

%======================================================================
\section{Introduction}
\label{sec:introduction}

@@

%=====================================================================
\section{VHDL-AMS}
\label{sec:vhdlams}

The VHDL-AMS language, defined by IEEE VHDL-AMS 1076.1, is the
industry standard mixed-signal high-level description language for
electronic and multi-domain systems.  VHDL-AMS, as an superset of
VHDL, supports modeling and simulation of \emph{analog} and
mixed-signal systems.

\subsection{Key Qualities of VHDL-AM}
\label{subsec:key-qualities-vhdl}

@@

@@

A simple low-pass filter is a passive RC network shown in
\autoref{fig:lowpassfig}.  According to the equation given above (see
\autoref{fig:transfun}), we can produce VHDL-AMS \emph{simultaneous
  statement} using \texttt{$s = d/dt = 'dot$} relation.  The
transformation looks as follows:
\begin{equation}
v_{in} = v_{out} + \tau_psv_{out} 
   \begin{array}[b]{c}                                                                                                                                    
      {\scriptscriptstyle s = d/dt}  \\=                                                                                                                  
   \end{array} 
v_{out} + \tau_p\cfrac{dv_{out}}{dt}
\begin{array}[b]{c}                                                                                                                                    
      {\scriptscriptstyle d/dt = } {\scriptscriptstyle 'dot} \\=                                                                                                                  
   \end{array}
  v_{in} = v_{out} + \tau_pv_{out}{'dot} 
\end{equation}

@@

Now we have equivalent equations:
\begin{equation}
  v_{in(i)}- v_{out(i)}=\tau_p(\frac{v_{out(i)}- v_{out(i-1)}}
  {\triangle t});
\end{equation}

\begin{equation}
  v_{out(i)}=v_{in(i)}(\frac{\triangle t}{\tau_p + \triangle t}) +
  v_{out(i-1)}(\frac{\tau_p}{\tau_p + \triangle t});                                                                \end{equation}

\begin{equation}
  v_{out(i)} 
 \begin{array}[b]{c}
   {\scriptscriptstyle \alpha= \triangle t / (\tau_p + \triangle t)}
   \\=
 \end{array}
 \alpha v_{in(i)} + (1- \alpha) v_{out(i-1)};                                                                           \end{equation}

@@

%===================================================================== 
\section{The Business Object Notation}
\label{sec:choiceobon}

@@

%=====================================================================
\section{Mapping between VHDL-AMS and BON}
\label{sec:mappingVB}

@@

\section{Refinement from VHDL-AMS to BON }
\label{sec:refVB} The main theme of this article is the translation
from VHDL-AMS to BON using refinement approach.  We will refine the
VHDL-AMS code up to the formal BON, and from this specification we
will generate an executable specification in the JML language.  For
this purpose, we will demonstrate our approach in BON-JML fashion
trought low-pass filter example.

@@

%=====================================================================
\section{Conclusion}
\label{sec:conclusion}

@@

\section {Acknowledgments} The research upon which this article is
based was caried out with sponsorship from Science Foundation Ireland
via the \textbf{UCD CASL SenseTile System} grant.

>>>>

%=============================================
%\thispagestyle{empty}
\begin{abstract}

@@

%=============================================
\section{Introduction}
\label{sec:introduction}

@@

%=============================================
\section{VHDL-AMS}
\label{sec:vhdlams}

The VHDL-AMS language, defined by IEEE VHDL-AMS 1076.1, is the
industry-standard mixed-signal high-level description language for
electronic and multi-domain systems.  VHDL-AMS, as an superset of
VHDL, supports modeling and simulation of \emph{analog} and
mixed-signal systems.  In short, one uses VHDL-AMS to describe
hardware components ranging in complexity from filters to CPUs.

\subsection{Key Qualities of VHDL-AMS}
\label{subsec:key-qualities-vhdl}

@@

A simple example will highlight some of the key aspects of VHDL-AMS
language and will be used to motivate and explain our refinement.

@@

A simple low-pass filter is a passive RC network shown in
\autoref{fig:lowpassfig}.  According to the equation given above (see
\autoref{fig:transfun}), we can produce VHDL-AMS \emph{simultaneous
  statement} using \texttt{$s = d/dt = 'dot$} relation\notej{I don't
  know what this means}.

The transformation looks like the following:
\begin{equation}
  v_{in} = v_{out} + \tau_psv_{out} 
  \begin{array}[b]{c}                                                                                                                {\scriptscriptstyle s = d/dt}  \\=                                                                                 \end{array} 
  v_{out} + \tau_p\cfrac{dv_{out}}{dt}
  \begin{array}[b]{c}
    {\scriptscriptstyle d/dt = } {\scriptscriptstyle 'dot} \\=
  \end{array}
  v_{in} = v_{out} + \tau_pv_{out}{'dot} 
\end{equation}

@@

Now we have equivalent equations:
\begin{equation}
  v_{in(i)}- v_{out(i)}=\tau_p(\frac{v_{out(i)}- v_{out(i-1)}}
  {\triangle t})
\end{equation}

\begin{equation}
  v_{out(i)}=v_{in(i)}(\frac{\triangle t}{\tau_p + \triangle t}) +
  v_{out(i-1)}(\frac{\tau_p}{\tau_p + \triangle t})                                                                \end{equation}

\begin{equation}
  v_{out(i)} 
 \begin{array}[b]{c}
   {\scriptscriptstyle \alpha= \triangle t / (\tau_p + \triangle t)}
   \\=
 \end{array}
 \alpha v_{in(i)} + (1- \alpha) v_{out(i-1)}                                                                           \end{equation}

@@

%=============================================
\section{The Business Object Notation}
\label{sec:choiceobon}

@@

%=============================================
\section{Mapping between VHDL-AMS and BON}
\label{sec:mappingVB}

@@

%=============================================  
\section{Refinement from VHDL-AMS to BON }
\label{sec:refVB} The main theme of this article is the translation
from VHDL-AMS to BON using refinement approach.  We will refine the
VHDL-AMS code up to the formal BON, and from this specification we
will generate an executable specification in the JML language.  For
this purpose, we will demonstrate our approach in BON-JML fashion
trought low-pass filter example.

@@

%=============================================
\section{Conclusion}
\label{sec:conclusion}

@@

\paragraph{Acknowledgments} The research upon which this article is
based was caried out with sponsorship from Science Foundation Ireland
via the \textbf{UCD CASL SenseTile System} grant.
